Where Do Population III Stars Form?

### 2018-10-24 paper.tex
update to paper: new figures, added results

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{mathtools}

@@

% Abstract of the paper
\begin{abstract}
This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the 
paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
keyword1 -- keyword2 -- keyword3
\end{keywords}

@@

Once a halo becomes chemically enriched by the death of its Pop III stars, then by definition, it can no longer form more Pop III stars. This marks the end of metal-free star formation in that pregalactic object. Understanding the mixing of metals into the environment of these halos is necessary to constrain the reach of these metals and the effects they have for future star formation. Numerical studies have shown that turbulence within halos can mix metals well down to their resolution limit \citep[][and more]{Wise08_Gal, Greif10}. Stars will continue to form in halos, but with an increased metal abundance, these stars are now labelled as metal-enriched stars. These stars still are considered metal-poor, relative to the solar abundance, and are observable in the universe. Understanding the formation and chemical abundance of second generation stars can provide more evidence and insight for the earlier generation of Pop III stars.

@@

Numerical simulations have also been employed to investigate collapse thresholds and Pop III star formation. \citet{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos. They derive a simple analytic expression for the mass threshold of halos given a particular LW flux. We will compare our results with this relation in future sections. \citet{yoshida03} also finds that cooling is inefficient in halos with a LW background > 0.01, although with sufficient \hh{} shielding, halos are able cool in the given LW background radiation. In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background flux of 10$^{-20}$. They find that \hh{} cooling is always a dominant process, even in large LW background fluxes. Assisting this result, \citet{OShea08} find that Pop III star formation can occur in relatively high LW backgrounds, implying that the LW background may not be a complete indicator of whether or not Pop III stars will form in a given halo.

@@

%====================================================================
\subsubsection{Pop III Star Formation and Feedback }
%====================================================================
The implemented Pop III star formation model is the same as in Wise \& Abel (2008). Each star particle represents a single star, and is formed in a cell when the following criteria are met: 
\begin{enumerate}
	\item a metallicity Z $\leq$ 5 $\times$ 10$^{-6}$ Z$_{\odot}$

@@

If within 1 pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells. The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
\begin{equation} \label{IMF}
	f(\log M)dM = M^{-1.3} \exp \Big[-\left( \frac{M_{\rm char}}{M}\right)^{1.6} \Big]dM
\end{equation}
where M$_{\rm char}$ = 20 M$_{\odot}$. This characteristic mass is different from W12 and W14 (would like to find a citation for this number, having a hard time tracking down some John had suggested). This results in an exponential cutoff before M$_{char}$ and a Salpeter IMF after. Once the cell meets the above criteria and the mass of the star is randomly determined from Eq. 3, an equal amount of gas is removed from the grid in a sphere which contains twice the stellar mass that is centered on the new star particle. The new Pop III star then gains the mass-weighted velocity of the gas contained within that sphere.

@@

%====================================================================
\section{Results}
%====================================================================
Possible other figures:
\begin{enumerate}
\item Jlw/J21 vs. Halo Mass colored by redshift - plotted with Machacek relation ??  - jlw\_mass\_machacek.png
\item Halo mass vs. redshift colored by total Jlw - plotted with background Machacek relation ?? - mass\_redshift\_machacek\_clocal.png
\end{enumerate}

\begin{figure}
	\includegraphics[width=\columnwidth]{images/hmf.png}
    \caption{Halo mass function of the last output of the simulation at $z$ = 9.3. The thick line is the analytic Sheth-Tormen mass function. The distribution of halo masses matches well with Sheth-Tormen until about 10$^{5}$ M$_{\odot}$.}
    \label{fig:hmf}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{images/mean_mass_errorb_fix.png}
    \caption{For halos hosting new Pop III stars, the mean halo mass is plotted versus redshift, in bins of $\Delta z$ = 1. The Machacek et al. minimum mass threshold is plotted for the constant LW background given in Eq. \ref{LWbg}. The mean halo masses fall below the relation until a redshift of 12.5, at which point the mean halo masses rise above the relation.}
    \label{fig:mean_mass}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{images/jlw_mass_machacek_total.png}
    \caption{The average LW background for host halos of new Pop III stars is plotted versus the host halo mass, colored by redshift. The Machacek et al. relation is plotted given the background LW in Eq. \ref{LWbg}. Almost all halos fall below the relation, across a range of redshifts. A few halos (or possibly a single halo) allow Pop III stars to form at a low halo mass in a very high LW background. There are a few halos that have Pop III stars forming at later times and at high halo masses.}
    \label{fig:jlw_mass_machacek}{}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{images/percent_below_dz1.png}
    \caption{The percentage of halos that form Pop III stars below the minimum mass threshold from \citet{Machacek01}, in bins of $\Delta z$ = 1. As seen in \ref{fig:jlw_mass_machacek}, almost all halos form below the mass threshold.}
    \label{fig:percent_below_dz1}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{images/totnump3_halomass_sidehist.png}
    \caption{Total number of Pop III stars in halos hosting new Pop III stars versus halo mass. A median number of four Pop III stars form in a single halo, with some forming as many as 16 Pop III stars.}
    \label{fig:totnump3_halomass_sidehist}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{images/totp3mass_halomass_sidehist.png}
    \caption{Total mass of Pop III stars in halos hosting new Pop III stars versus halo mass. Lines of constant star formation efficiencies are overplotted. Most halos form Pop III stars at efficiencies between 10$^{-3}$ and 10$^{-4}$.}
    \label{fig:totp3mass_halomass_sidehist}
\end{figure}

%====================================================================
\subsection{Population III host halo masses}
%====================================================================

@@

>>>>

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{mathtools}
\usepackage{hyperref}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Abstract of the paper
\begin{abstract}
We perform a cosmological simulation with a comoving volume of 1 Mpc$^{3}$ to study the birthplaces of Population III stars, using the adaptive mesh refinement code \enzo{}. We investigate the distribution of host halo masses and its relationship to the Lyman-Werner background intensity.  In our sample of 697 host halos, we find that 84\% of them have masses below the Machacek et al. (2001) relation because of the inclusion of \hh{} self-shielding.  In our simulation above a redshift of 12.5, the mean halo mass is time-independent and ~10$^{5.8}$ M$_{\odot}$. Afterwards, it steadily rises above the Machacek et al. relation to a mean value of ~10$^{6.6}$ M$_{\odot}$. Most of these halos form multiple Population III stars, with a median number of four, up to a maximum of 16. We also find that a few halos do form stars below the Machacek et al. relation but in a high Lyman-Werner radiation field with values up to ~50 J$_{21}$. Our results suggest that Population III star formation may be less affected by Lyman-Werner radiation feedback than previously thought and that Population III multiple systems are common.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
star formation -- methods:numerical -- cosmology
\end{keywords}

@@

Once a halo becomes chemically enriched by the death of its Pop III stars, then by definition, it can no longer form more Pop III stars. This marks the end of metal-free star formation in that pregalactic object. Understanding the mixing of metals into the environment of these halos is necessary to constrain the reach of these metals and the effects they have for future star formation. Numerical studies have shown that turbulence within halos can mix metals well down to their resolution limit \citep[][and more]{Wise08_Gal, Greif10}. Stars will continue to form in halos, but with an increased metal abundance, these stars are now labeled as metal-enriched stars. These stars still are considered metal-poor, relative to the solar abundance, and are observable in the universe. Understanding the formation and chemical abundance of second generation stars can provide more evidence and insight for the earlier generation of Pop III stars.

@@

Numerical simulations have also been employed to investigate collapse thresholds and Pop III star formation. \citet[hereafter M01]{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos. They derive a simple analytic expression for the mass threshold of halos given a particular LW flux:
\begin{equation} \label{mthresh}
	M_{TH} ( M_{\odot} ) = 1.25 \times 10^{5} + 8.7  \times 10^{5} \left( \frac{4 \pi J_{LW}}{10^{-21}} \right)^{.47}
\end{equation}
We will compare our results with this relation in future sections. \citet{yoshida03} also finds that cooling is inefficient in halos with a LW background > 0.01, although with sufficient \hh{} shielding, halos are able cool in the given LW background radiation. In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background flux of 10$^{-20}$. They find that \hh{} cooling is always a dominant process, even in large LW background fluxes. Assisting this result, \citet{OShea08} find that Pop III star formation can occur in relatively high LW backgrounds, implying that the LW background may not be a complete indicator of whether or not Pop III stars will form in a given halo.

@@

%====================================================================
\subsubsection{Pop III Star Formation and Feedback }
%====================================================================
The implemented Pop III star formation model is the same as in \citet{Wise08_Gal}. Each star particle represents a single star, and is formed in a cell when the following criteria are met: 
\begin{enumerate}
	\item a metallicity Z $\leq$ 5 $\times$ 10$^{-6}$ Z$_{\odot}$

@@

If within 1 pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells. The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
\begin{equation} \label{IMF}
	f(\log M)dM = M^{-1.3} \exp \Big[-\left( \frac{M_{\rm char}}{M}\right)^{1.6} \Big]dM
\end{equation}
where M$_{\rm char}$ = 20 M$_{\odot}$ \citep{Hirano17}. This characteristic mass is different from W12 and W14 (would like to find a citation for this number, having a hard time tracking down some John had suggested). This results in an exponential cutoff before M$_{char}$ and a Salpeter IMF after. Once the cell meets the above criteria and the mass of the star is randomly determined from Eq. 3, an equal amount of gas is removed from the grid in a sphere which contains twice the stellar mass that is centered on the new star particle. The new Pop III star then gains the mass-weighted velocity of the gas contained within that sphere.

@@

%====================================================================
\section{Results}
%====================================================================
In this section, we will present the distribution of host halo masses of Pop III stars, the relation between the mass distribution and the LW background radiation, and the distribution of various Pop III properties.

%====================================================================
\subsection{Population III host halo masses}
%====================================================================
To ensure that our box is representative of a typical piece of the universe, the numerical halo mass function is plotted along with the analytic Sheth-Tormen mass function at $z$ = 9.3 in Fig. \ref{fig:hmf}. The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve lower mass halos.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/hmf.pdf}
    \caption{Halo mass function of the last output of the simulation at $z$ = 9.3. The thick, black line is the analytic Sheth-Tormen mass function. The distribution of halo masses matches well with Sheth-Tormen until about 10$^{5}$ M$_{\odot}$.}
    \label{fig:hmf}
\end{figure}

As mentioned previously, Pop III stars form in our simulation only between 27.23 $\leq z \geq$ 9.39. During this time frame, a total of 697 Pop III stars form. The corresponding star formation rate density can be seen in Figure \ref{fig:pop3_SFR_bar}. To determine the host halos of new Pop III stars, the halo finding code, \rockstar{} \citep{rockstar}, is used. The mass determined by \rockstar{} is the dark matter mass, so to get the baryonic mass of the halos, we multiply the masses by $\Omega_{M}$/$\Omega_{DM}$. The baryonic mass is subsequently used in our analysis. The center and virial radius of each halo is also pulled from \rockstar{}. A small percentage of Pop III stars do not form in a halo found by \rockstar{}. Assuming that Pop III stars should be forming in collapsed halos, we calculate the virial mass and radius of a halo centered on the Pop III star as an approximation. The LW background intensity is calculated by summing up the LW intensity coming from each radiating star particle outside the virial radius of the host halo. This is then added to the constant LW background implemented in the simulation (Eq. \ref{LWbg}).

@@

Binning the data in $\Delta z$ = 1, the mean halo mass hosting Pop III stars is determined, and plotted against the redshift bins in Figure \ref{fig:mean_mass}. Equation \ref{mthresh} is plotted using the LW background intensity in Eq. \ref{LWbg}. Notably, the mean halo mass falls well below the relation until $z$ = 12.5. Below the mass threshold, the mean halo mass is 10$^{5.89}$ M$_{\odot}$, and rises to 10$^{6.6}$ M$_{\odot}$ after $z$ = 12.5. The large discrepancy between our data and the mass threshold from M01 is indicative of the \hh{} shielding which is included in our simulation. \hh{} shielding allows for halos to form at much lower masses, and therefore, Pop III stars are forming in these halos at early times. In the analysis done in M01, \hh{} shielding is neglected in their calculations for a variety of reasons, including the Doppler broadening of LW bands and large column densities of \hh{} only beginning to form at late times. Interestingly, a full radiative transfer simulation, such as ours, does not produce identical results as M01 predicts. Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[e.g.]{yoshida03, Ricotti01, Glover01, Hartwig15}.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/mean_mass_errorb_fix.pdf}
    \caption{For halos hosting new Pop III stars, the mean halo mass for redshift bins of $\Delta z$ = 1 is plotted along the left hand side versus redshift. The black scatter points indicate the mean halo mass for that redshift bin and the x indicate the median halo mass. The error bars indicate the 15.1\% and 84.1\% percentiles. Plotted along the right hand side is the percentage of halos that fall below the M01 mass threshold, also plotted along redshift. The M01 mass threshold (Eq. \ref{mthresh}), is plotted for the constant LW background in Eq. \ref{LWbg}. Almost all halos fall below the M01 relation, until $z$ = 12.5, when the mean halo mass rises above the relation.}
    \label{fig:mean_mass}
\end{figure},

The LW background intensity is plotted versus the halo mass for each host Pop III halo in our dataset in Figure \ref{fig:jlw_mass_machacek}. Each point is colored by the redshift where the Pop III star forms and the mass threshold from M01 (Eq. \ref{mthresh}) for the given LW background (Eq. \ref{LWbg}) is also plotted. We see that almost all halos form below the M01 threshold. There are also a few halos that form in very high J$_{LW}$, below the relation. It should be noted that there may be duplicate halos within this plot, since halos are allowed to form multiple Pop III stars if the conditions are sufficient. The grouped points in the higher end of J$_{LW}$ may be representative of such halos. We find that 84\% of the halos forming new Pop III stars lie below the M01 mass threshold.

@@

We can also look at the number of Pop III stars and the total mass of Pop III stars per halo. The number of Pop III stars per halo is plotted against the halo mass in Figure \ref{fig:totnump3_halomass_sidehist} as a 2D-histogram. The histogram of the number of Pop III stars is projected on the right. We find that a median number of four Pop III stars form per halo, with a maximum of 16 Pop III stars forming per halo. Since we did not restrict the number of Pop III stars that can form in a halo, we find that the conditions are often sufficient for multi-Pop III stars to form in a single system. The total mass of Pop III stars per halo is plotted against halo mass in \autoref{fig:totp3mass_halomass_sidehist}. The histogram of the total Pop III mass is projected on the right. Lines of constant star formation efficiency are overplotted. We find that most of our Pop III stars are forming between 10$^{-4}$ < f$_\star$ < 10$^{-3}$.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/jlw_mass_machacek_total.pdf}
    \caption{The average LW background for host halos of new Pop III stars is plotted versus the host halo mass, colored by redshift. The Machacek et al. relation is plotted given the background LW in Eq. \ref{LWbg}. Almost all halos fall below the relation, across a range of redshifts. A few halos (or possibly a single halo) allow Pop III stars to form at a low halo mass in a very high LW background. There are a few halos that have Pop III stars forming at later times and at high halo masses.}
    \label{fig:jlw_mass_machacek}{}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{images/totnump3_halomass_sidehist.pdf}
    \caption{Total number of Pop III stars in halos hosting new Pop III stars versus halo mass. A median number of four Pop III stars form in a single halo, with some forming as many as 16 Pop III stars.}
    \label{fig:totnump3_halomass_sidehist}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{images/totp3mass_halomass_sidehist.pdf}
    \caption{Total mass of Pop III stars in halos hosting new Pop III stars versus halo mass. Lines of constant star formation efficiencies are overplotted. Most halos form Pop III stars at efficiencies between 10$^{-3}$ and 10$^{-4}$.}
    \label{fig:totp3mass_halomass_sidehist}
\end{figure}
